Cycles of the logistic map

### 2013-04-30 doc/pc-ijbc.tex
edit till sec. 2.4

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting cyclic polynomials formed by periodic orbit points.
The minimal polynomials of the critical parameters
  of the logistic, H\'enon, and cubic maps are obtained
  for $n$ up to 13, 9, and 8,
  respectively.
%
%}
\end{abstract}

@@

Consider the logistic map \cite{may, strogatz}:
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv r \, x_k \, ( 1 - x_k ).
\label{eq:logmap}
\end{equation}
%
If we iterate \refeq{logmap} from $k = 0$,
what does the resulting sequence $x_0$,
  $x_1 = f(x_0)$,
  $x_2 = f(x_1)$, $\ldots$ look like?
%
%
%
We can visualize the sequence on the cobweb plot,
  see \reffig{cobweb} for examples.
%
Starting from $(x_0, x_0)$ on the diagonal,
  each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
  where $y = f(x_k) = x_{k+1}$;
the next horizontal arrow then reflects $(x_k, y)$ to
  $(y, y) = (x_{k+1}, x_{k+1})$,
  which starts the next iteration.

\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
    \end{center}
  \end{minipage}%
  \caption{\label{fig:cobweb}
  Cobweb plot of the logistic map.}
\end{figure}

Three outcomes are possible:
  (i) a \emph{fixed point},
      which is a constant (including infinity),
      e.g., \reffig{cobweb}(a);
  (ii) a periodic \emph{cycle},
      which is a self-repeating pattern,
      e.g., \reffigs{cobweb}(b)-(e);
%On the cobweb plot, an $n$-cycle is a loop of $2n$ segments.
or
  (iii) a chaotic trajectory,
      e.g., \reffig{cobweb}(f).
We will focus on the first two cases here.

A fixed point is a solution of $x^* = f(x^*)$.
%
If $x_0$ deviates slightly from $x^*$
  and the sequence still converges to $x^*$,
  we call it \emph{stable}.
%
For a differentiable $f$,
  a stable fixed point requires $|f'(x^*)| \le 1$
  to reduce deviations in successive iterations \cite{strogatz}.

In an $n$-cycle, $n$ is the smallest positive integer
  that allows $x_1 = x_{n+1} = f^n(x_1)$,
  where $f^n$ is the $n$th iterate of $f$,
  e.g., $f^3(x) = f(f(f(x)))$.
Thus, any $x_k$ in an $n$-cycle of $f$ must be a fixed point of $f^n$
%
\big[the reverse is, however, untrue, for a fixed point of $f^n$
  can also be a fixed point of $f^d$ as long as $d|n$:
  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
%
%
We can therefore classify a cycle as stable or unstable
  by the corresponding fixed point of $f^n$:
  a stable cycle requires
  $\big| \frac {d} {dx} f^n(x_1) \big| \le 1$,
  or by the chain rule,
%
%
%
\begin{equation}
  \Big| f'(x_1) \dots f'(x_n) \Big| \le 1,
\label{eq:der}
\end{equation}
where $x_1. \ldots, x_n$ are the $n$ points within the cycle, or the orbit.
Further, the onset and bifurcation points
  are defined at the loci
  where $\frac {d} {dx} f^n(x_1)$ reaches $+1$ and $-1$,
  respectively \cite{strogatz}.
%
%
%

The outcome of the iterated sequence of course
  depends on the parameter $r$.
%
Below we will present an algorithm to identify
  all regions of $r$ that allow stable $n$-cycles.
%We ask,
%  by which $r$ values can a stable $n$-cycle exist?
%

@@

To simplify the calculation, we first change variables \cite{saha} by
%
%\begin{equation}
\[
    x^{\mathrm{new}} \leftarrow r(x^{\mathrm{old}} - 1/2),
    \quad R \leftarrow r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{\mathrm{new}}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of the polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

We solve the problem in two steps.
Since the $n$-cycles form a subset of the fixed points of $f^n$,
we will first find
  the polynomials at the stability boundaries of
  the fixed points of $f^n$
  (\refsecs{cyclic} to \ref{sec:examples}),
then remove contributions from shorter $d$-cycles ($d|n$)
  (\refsecs{primfac} and \ref{sec:degprimfac}).

Let us consider the first step of finding the fixed points of $f^n$.
At the first glance, the problem can be tackled by brute force:
  we can solve
  %the $n$ equations
  \refeqs{logmaps} and express $x_1, \ldots, x_n$
  in terms of $R$,
  and then plug the solution into \req{der}.
The result contains $R$ only (no $x_k$),
  and is therefore the answer.
But since \refeqs{logmaps} are nonlinear,
  it quickly becomes impossible for $n > 2$,
  as the degree of polynomials grows exponentially;
  thus it is nontrivial to reduce the final equation of $R$
  into a polynomial one.
Nonetheless, on a computer, one can
  construct a Gr\"obner basis \cite{kk1}
  to automate the reduction.
%
The approach, albeit straightforward, does not
  exploit the cyclic structure of \refeqs{logmaps},
can thus be improved by the following alternative.

Instead of solving \refeqs{logmaps} for $x_k$,
  we will derive a set of \emph{homogeneous linear} equations
  $\sum_j A_{ij} C_j = 0$
  regarding cyclic polynomials $\{C_j\}$ of $x_k$
  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
%
Now the matrix formed by the coefficients $A_{ij}$ of the equations
  must have a zero determinant,
  for the cyclic polynomials $\{C_j\}$ are not zeros altogether.
%
%As the coefficients are polynomials of $R$ only,
Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
  the needed polynomial equation of $R$,
whose roots contain all fixed points of $f^n$.
This completes the first step.
%
%Note that we will obtain different equations
%  at the onset and bifurcation points
%  because the coefficients,
%  hence the matrices and determinants,
%  will be different.
%

For the second step,
we show
that short cycles serve as
factors in the polynomials obtained above,
and thus can be readily factored out.

@@

A polynomial is cyclic if it is invariant
  under the cycling of variables
  $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
  \ldots, x_n \rightarrow x_1$,
  e.g., $a(\vx) = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
  and $b(\vx) = x_1 x_3 + x_2 x_4$,
  for $n = 4$, where $\vx \equiv \{x_1, \ldots, x_n\}$.
A cyclic polynomial should not to be confused with a symmetric polynomial,
  which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
  e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
  but $a(\vx) + b(\vx)$ is.

@@

We now consider cyclic polynomials
  generated from a monomial of unit coefficient,
  such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$.
They can be systematically labeled as follows.
We pick the monomial generator,
  which can be written as
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  then form a sequence $p$ of indices with
  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s;
  the corresponding cyclic polynomial is denoted by $C_p(\vx)$,
e.g.,
  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
We omit the length $n$ in this notation,
  for we will mostly work with a fixed $n$ at a time.
Since a cyclic polynomial can have multiple generators,
  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
   (assuming $n \ge 3$),
  we pick the one that corresponds to
  the smallest $p$
  in the sense of lexicographic order,
  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$,
  because $12 < 23$.
Finally, we add $C_0(\vx) \equiv 1$ for completeness.
%
%
%

\subsection{Square-free cyclic polynomials}

We further restrict ourselves to
  a subset of square-free cyclic polynomials,
  which have no square or higher powers of any $x_k$,
  e.g., $C_{12}(\vx) = x_1 x_2 + \dots$ is square-free,
  $C_{112}(\vx) = {x_1}^2 x_2 + \dots$ is not,
see \reftab{sqrfreepoly} for more examples.
Obviously, the label $p$ of a square-free polynomial
  has no repeated index.
We denote the set of all square-free $p$ by
$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$
%  ($n \ge 4$),
such that its size $|\Bset|$ equals the number $\NB$ of
  square-free cyclic polynomials.

\begin{table}[h]\footnotesize
\tbl{
Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
%\begin{center}
{
\begin{tabular}{c c c c c}
\hline
$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
\hline
0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
1             & $x_1 + x_2 + \dots + x_n$
              & $x_1$ (or $x_2$, \ldots)
              & $10\ldots0$
              & $\{1\}$ (or $\{2\}$, \ldots) \\
12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
              & $110\ldots0$
              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
              & $1010\ldots0$
              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
$\vdots$      & $\vdots$ \\
123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
              & $1110\ldots0$
              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
              & $11010\ldots0$
              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
$\vdots$      & $\vdots$ \\
$12\dots n$  & $x_1 x_2 \dots x_n$
              & $x_1 x_2 \dots x_n$
              & $11\ldots1$
              & $\{1, 2, \ldots, n\}$  \\
\hline
\multicolumn{5}{p{\linewidth}}{
$^\dagger$ Alternative generators are shown in parentheses.
}\\
\multicolumn{5}{p{\linewidth}}{
$^\ddagger$ The corresponding binary necklaces.
}\\
\multicolumn{5}{p{\linewidth}}{
$^*$ The label $p$ of a square-free cyclic polynomial
    has no repeated indices;
    so the indices can be cast to a set.
}\\
\hline
\end{tabular}
\label{tab:sqrfreepoly}
}
%\end{center}
\end{table}

We first show that
  the square-free cyclic polynomials
  serve as a basis for expanding cyclic polynomials:

\begin{theorem}
  For the logistic map \refeq{logmaps},
  any cyclic polynomial $K(\vx)$
  formed by the $n$-cycle points
  $\vct x = \{x_1, \ldots, x_n\}$
  is a linear combination of
the square-free cyclic polynomials $C_p(\vx)$:
\[
  K(\vx) = \sum_{p \in \Bset} f_p(R) \, C_p(\vx),
\]
  where $\Bset = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
  the set of indices of all square-free cyclic polynomials,
  and $f_p(R)$ are polynomials of $R$.
  \label{thm:sqrfree}
\end{theorem}

\begin{proof}
We show the theorem by the following square-free reduction.
%
Given a cyclic polynomial $K(\vx)$,
  we recursively apply \refeq{logmaps} as
  $x_k^2 \rightarrow R - x_{k+1}$,
  until all squares or higher powers of $x_k$ are eliminated.
The process will not last indefinitely
  for each substitution reduces the degree in $x_k$ (no matter which $k$)
  by one.
Since the original polynomial is cyclic,
  so is the reduced one.
All terms that involve no $x_k$
  are collected to serve as the coefficient before $C_0(\vx)$, which is 1.
Since no square or higher powers of $x_k$
  can survive the reduction,
  all cyclic polynomials in the final result
  are square-free.
The coefficients are polynomials of $R$,
  for $R$ is the only variable introduced by the substitutions.
\end{proof}

@@

\refthm{sqrfree}
  shows that any cyclic polynomial
  can be expanded
  as a combination of the square-free ones,
  which serve as a basis.
Below we show that at the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$ are themselves
  linearly connected by an $\NB \times \NB$ matrix equation.
The determinant of matrix must vanish,
  and this condition yields the solution of the problem.

@@

Since a set of homogeneous linear equations
  has a non-trivial solution
  only if the determinant of the coefficient matrix
  is zero, we have
\begin{equation}
  A_n\RX \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
\label{eq:xr}
\end{equation}
Here we have defined $A_n\RX$ as a polynomial of $R$ and $\lambda$,
  and we have also attached the subscript $n$,
  for later use with $A_d\RX$, where $d$ are divisors of $n$.
\refeq{xr} is a necessary condition
  since $C_p(\vx)$ cannot vanish altogether;
and since it involves $R$ only,
  the polynomial expansion of the determinant
  gives the answer to our problem.
%Note that we did not solve the values $C_p$ in the process.

To summarize, we have
\begin{theorem}
  At the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$
  are linear related by \refeq{xcp}, with
  $\lambda$ being $+1$ and $-1$, respectively,
  and $T_{pq}(R)$ the coefficients
  from the square-free reduction of $\Lambda(\vx) \, C_p(\vx)$
  with $\Lambda(\vx)$ specified by \refeq{logder}.
  Thus, $R$ at the two points are the roots of the
  polynomials $A_n(R, \lambda = \pm1)$
  obtained from the characteristic equation \refeq{xr}.
  \label{thm:main}
\end{theorem}

\begin{remark}
%\begin{remark}[1]
  For complex $R$ and $\vx$,
  $\lambda$ should be generalized from $\pm1$
  to any $\lambda = \exp(i\theta)$,
  where $\theta \in [0, 2\pi]$,
  the algorithm still applies.
  By increasing $\theta$ from 0 to $2\pi$,
  we can trace a two-dimensional region of a complex $R$
  for stable cycles.
  These regions are bulbs in the Mandelbrot set,
  %(however, we need the replacement
  %$x_k \rightarrow -z_k$
  %and
  %$R \rightarrow -c$)
  see ref. \cite{stephenson} and \reffig{logbulb}.

  Further, with $\lambda = 0$,
  the algorithm determines the superstable point,
  at which the deviation from a cycle point vanishes
  to the linear order after $n$ iterations of $f$.
  But we have a better algorithm in this case:
  since at least one of the $x_k$ is zero by \refeq{logder},
  then $f^n(x_k = 0) = x_{n+k} = 0$ provides
  the needed polynomial equation of $R$ \cite{strogatz}.
\end{remark}

@@

The algorithm was coded into a Mathematica program,
which was used to compute the polynomials for $n$ up to 13.
The polynomials for a general $\lambda$
and those at $\lambda = \pm1$ (onset and bifurcation points) are listed
in \reftab{Anlog} and \reftab{Pnlog}, respectively, for some small $n$.
%
For complex $R$, $\lambda$, and $\vx$,
the method can also compute the region of stability for $R$,
with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
  instead of $\pm1$;
the results are shown in \reffig{logbulb}
for $n$ up to $8$.
%
For polynomials of larger $n$, see the website in \refsec{end}.
The representative $r$ values are listed in \reftab{rval}.

@@

\begin{remark}
The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
%
On the complex domain, however, we can have a $c$-fold branching with $c>2$,
  which corresponds to a contact points between ``bulbs''
  in the Mandelbrot set, see \reffig{logbulb}.
\end{remark}

>>>>

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting the cyclic polynomials of the periodic orbit points.
The minimal polynomials of the critical parameters
  of the logistic, H\'enon, and cubic maps are obtained
  for $n$ up to 13, 9, and 8,
  respectively.
%
%}
\end{abstract}

@@

Consider the logistic map \cite{may, strogatz}:
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv r \, x_k \, ( 1 - x_k ).
\label{eq:logmap}
\end{equation}
%
If we iterate \refeq{logmap} from $k = 1$,
the resulting sequence $x_1$,
  $x_2 = f(x_1)$,
  $x_3 = f(x_2)$, $\ldots$
can be conveniently visualized on the cobweb plot,
  as shown in \reffig{cobweb}.
%
Starting from $(x_1, x_1)$ on the diagonal,
  each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
  where $y = f(x_k) = x_{k+1}$;
the next horizontal arrow then reflects $(x_k, y)$ to
  $(y, y) = (x_{k+1}, x_{k+1})$,
  which starts the next iteration.
%
%
\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
    \end{center}
  \end{minipage}%
  \caption{\label{fig:cobweb}
  Cobweb plot of the logistic map.}
\end{figure}
%
%
After many iterations, there are three ultimate patterns:
  (i) a \emph{fixed point},
      which is a constant (including infinity),
      e.g., \reffig{cobweb}(a);
  (ii) a periodic \emph{cycle},
      which is a self-repeating pattern,
      e.g., \reffigs{cobweb}(b)-(e);
%On the cobweb plot, an $n$-cycle is a loop of $2n$ segments.
or
  (iii) a chaotic trajectory,
      e.g., \reffig{cobweb}(f).
We will focus on the first two cases here.

A fixed point is a solution of $x^* = f(x^*)$.
%
If $x_1$ deviates slightly from $x^*$
  and the sequence still converges to $x^*$,
  then it is \emph{stable}.
%
For a differentiable $f$,
  a stable fixed point requires $|f'(x^*)| \le 1$
  to reduce deviations in successive iterations \cite{strogatz}.

In an $n$-cycle, $n$ is the smallest positive integer
  that allows $x_1 = x_{n+1} = f^n(x_1)$,
  where $f^n$ is the $n$th iterate of $f$,
  e.g., $f^3(x) = f(f(f(x)))$.
Thus, any $x_k$ in an $n$-cycle of $f$ must be a fixed point of $f^n$
%
\big[the converse is, however, untrue, for a fixed point of $f^n$
  can also be a fixed point of $f^d$ as long as $d|n$:
  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
%
%
and a cycle can be classified as stable or unstable
  according to the corresponding fixed point of $f^n$:
  a stable cycle requires
  $\big| \frac {d} {dx} f^n(x_1) \big| \le 1$,
  or by the chain rule,
%
%
%
\begin{equation}
  \Big| f'(x_1) \cdots f'(x_n) \Big| \le 1,
\label{eq:der}
\end{equation}
where $x_1. \ldots, x_n$ are the $n$ points within the cycle, or the orbit.
Further, the onset and bifurcation points
  are defined at the loci
  where $\frac {d} {dx} f^n(x_1)$ reaches $+1$ and $-1$,
  respectively \cite{strogatz}.
%
%
%
The orbit and cycle stability depend on the parameter $r$.
%
Below we will present an algorithm to identify
  all regions of $r$ that allow stable $n$-cycles.

@@

To simplify the calculation, we first change variables \cite{saha} by
%
%\begin{equation}
\[
    x^{\mathrm{new}} \equiv r(x^{\mathrm{old}} - 1/2),
    \quad R \equiv r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{\mathrm{new}}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of some polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

@@

Since the $n$-cycles constitute a subset of the fixed points of $f^n$,
we will first find
  the polynomials at the stability boundaries
  for the fixed points of $f^n$
  (\refsecs{cyclic} to \ref{sec:examples}).
The contributions from shorter $d$-cycles ($d|n$)
  are lower-degree factors of the polynomials,
  and can be readily removed
  (\refsecs{primfac} and \ref{sec:degprimfac}).

At the first glance, the polynomials of the fixed points of $f^n$
  can be obtained by brute force.
We can solve
  \refeqs{logmaps} and express $x_1, \ldots, x_n$
  in terms of $R$,
  and then plug the solution into \req{der}.
The result would contain $R$ only,
  and is therefore the answer.
But since \refeqs{logmaps} are nonlinear,
  it is nontrivial to reduce the final equation of $R$
  into a polynomial form.
Nonetheless, on a computer, one can
  construct a polynomial Gr\"obner basis \cite{kk1}
  that gradually eliminates $x_k$ out of the $n+1$ equations.
As a special case, if $x_2, \dots, x_n$ are eliminated first,
  the final elimination of $x_1$ can be accomplished
  by setting the resultant of $f^n(x_1) = x_1$ and
  \refeq{der} or $\frac{d}{dx}f^n (x_1) = \pm 1$
  to zero \cite{burm},
  which furnishes the needed polynomial equation of $R$.
%
These approaches, however, do not
  exploit the cyclic structure of \refeqs{logmaps},
  and can thus be improved by the following alternative.

Instead of solving \refeqs{logmaps} for $x_k$,
  we will derive a set of \emph{homogeneous linear} equations
  $\sum_j A_{ij} C_j = 0$
  regarding cyclic polynomials $\{C_j\}$ of $x_k$
  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
%
Now the matrix formed by the coefficients $A_{ij}$ of the equations
  must have a zero determinant,
  for the cyclic polynomials $\{C_j\}$ are not zeros altogether.
%
%As the coefficients are polynomials of $R$ only,
Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
  the needed polynomial equation of $R$,
whose roots contain all fixed points of $f^n$.
%
%Note that we will obtain different equations
%  at the onset and bifurcation points
%  because the coefficients,
%  hence the matrices and determinants,
%  will be different.
%

@@

A polynomial is cyclic if it is invariant
  under the cycling of variables
  $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
  \ldots, x_n \rightarrow x_1$,
  e.g., $a(\vx) = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
  and $b(\vx) = x_1 x_3 + x_2 x_4$,
  where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
Note that a cyclic polynomial is not necessarily a symmetric one,
  which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
  e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
  but $a(\vx) + b(\vx)$ is.

@@

Cyclic polynomials
  generated from monomials of unit coefficient
  [such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$]
  can be labeled as follows.
We first write the monomial generator as
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  then the sequence $p$ of indices with
  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
  serves as the label of the cyclic polynomial $C_p(\vx)$.
For example,
  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
The cycle length $n$ is omitted for convenience.
%  for we will mostly work with a fixed $n$ at a time.
In case the cyclic polynomial has several generators,
%  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
%   (assuming $n \ge 3$),
  we pick the one with the smallest $p$
  in the sense of lexicographic order,
  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$
  because $12 < 23$ ($n \ge 3$).
Finally, we add $C_0(\vx) \equiv 1$ for completeness.
%
%
%

\subsection{Square-free reduction}

We now consider
  a subset of \emph{square-free} cyclic polynomials,
  which have no square or higher powers of $x_k$.
For example, $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
  $C_{112}(\vx) = {x_1}^2 x_2 + \cdots$ is not.
%see \reftab{sqrfreepoly} for more examples.
The label $p$ of a square-free polynomial
  has no repeated index.
The set of all square-free $p$ is denoted by
$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
and its size $|\Bset|$ equals the number $\NB$ of
  square-free cyclic polynomials.
%
%
The square-free cyclic polynomials
  furnish a basis for expanding cyclic polynomials:

%\begin{table}[h]\footnotesize
%\tbl{
%Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
%%\begin{center}
%{
%\begin{tabular}{c c c c c}
%\hline
%$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
%\hline
%0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
%1             & $x_1 + x_2 + \dots + x_n$
%              & $x_1$ (or $x_2$, \ldots)
%              & $10\ldots0$
%              & $\{1\}$ (or $\{2\}$, \ldots) \\
%12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
%              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
%              & $110\ldots0$
%              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
%13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
%              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
%              & $1010\ldots0$
%              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
%$\vdots$      & $\vdots$ \\
%123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
%              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
%              & $1110\ldots0$
%              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
%124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
%              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
%              & $11010\ldots0$
%              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
%$\vdots$      & $\vdots$ \\
%$12\dots n$  & $x_1 x_2 \dots x_n$
%              & $x_1 x_2 \dots x_n$
%              & $11\ldots1$
%              & $\{1, 2, \ldots, n\}$  \\
%\hline
%\multicolumn{5}{p{\linewidth}}{
%$^\dagger$ Alternative generators are shown in parentheses.
%}\\
%\multicolumn{5}{p{\linewidth}}{
%$^\ddagger$ The corresponding binary necklaces.
%}\\
%\multicolumn{5}{p{\linewidth}}{
%$^*$ The label $p$ of a square-free cyclic polynomial
%    has no repeated indices;
%    so the indices can be cast to a set.
%}\\
%\hline
%\end{tabular}
%\label{tab:sqrfreepoly}
%}
%%\end{center}
%\end{table}

\begin{theorem}
  For the logistic map \refeq{logmaps},
  any cyclic polynomial $K(\vx)$
  formed by the $n$-cycle points
  $\vct x = \{x_1, \ldots, x_n\}$
  is a linear combination of
the square-free cyclic polynomials $C_p(\vx)$:
\[
  K(\vx) = \sum_{p \in \Bset} f_p(R) \, C_p(\vx),
\]
  where $\Bset$ % = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
  is the set of indices of all square-free cyclic polynomials,
  and $f_p(R)$ are polynomials of $R$.
  \label{thm:sqrfree}
\end{theorem}

\begin{proof}
Consider the following square-free reduction.
%
Given a cyclic polynomial $K(\vx)$,
  we recursively apply \refeq{logmaps} as
  $x_k^2 \rightarrow R - x_{k+1}$,
  until all squares or higher powers of $x_k$ are eliminated.
The process will not last indefinitely
  for each substitution reduces the degree in $x_k$ %(no matter which $k$)
  by one.
Since the original polynomial is cyclic,
  so is the reduced one, which is also square-free.
All terms that involve no $x_k$
  are collected to serve as the coefficient before $C_0(\vx) \equiv 1$.
%Since no square or higher powers of $x_k$
%  can survive the reduction,
%  the final cyclic polynomials are square-free;
The coefficients $f_p$ are polynomials of $R$,
  for $R$ is the only variable introduced by the substitutions.
\end{proof}

@@

\refthm{sqrfree}
  shows that any cyclic polynomial
  can be expanded
  as a combination of the square-free ones,
  which serve as a basis.
Below we show that at the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$ are themselves
  linearly connected by $\NB$ homogeneous equations.
The matrix of the connecting coefficients must have a zero determinant,
  which yields the desired polynomial.

@@

Since a set of homogeneous linear equations
  has a non-trivial solution
  only if the determinant of the coefficient matrix
  is zero, we have
\begin{equation}
  A_n\RX \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
\label{eq:xr}
\end{equation}
Here, $A_n\RX$ is a polynomial of $R$ and $\lambda$,
  and the subscript $n$ is attached such that 
  it can be used later with $A_d\RX$ of divisors $d$ of $n$.
\refeq{xr} is a necessary condition
  since $C_p(\vx)$ cannot vanish altogether;
and since it involves $R$ only,
  the polynomial expansion of the determinant
  gives the answer to our problem.
%Note that we did not solve the values $C_p$ in the process.

To summarize, we have
\begin{theorem}
  At the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$
  are linear related by \refeq{xcp}, with
  $\lambda$ being $+1$ and $-1$, respectively,
  and $T_{pq}(R)$ are the coefficients
  from the square-free reduction of $\Lambda(\vx) \, C_p(\vx)$
  with $\Lambda(\vx)$ specified by \refeq{logder}.
  Thus, $R$ at the two points are the roots of the
  polynomials $A_n(R, \lambda = \pm1)$
  obtained from the characteristic equation \refeq{xr}.
  \label{thm:main}
\end{theorem}

\begin{remark}
%\begin{remark}[1]
  For complex $R$ and $\vx$,
  $\lambda$ should be generalized from $\pm1$
  to any $\lambda = \exp(i\theta)$,
  where $\theta \in [0, 2\pi]$,
  the algorithm still applies.
  By increasing $\theta$ from 0 to $2\pi$,
  we can trace a two-dimensional region of a complex $R$
  for stable cycles.
  These regions are bulbs in the inverted Mandelbrot set,
  %(however, we need the replacement
  %$x_k \rightarrow -z_k$
  %and
  %$R \rightarrow -c$)
  see ref. \cite{stephenson}. % and \reffig{logbulb}.

  Further, with $\lambda = 0$,
  the algorithm determines the superstable point,
  at which the deviation from a cycle point vanishes
  to the linear order after $n$ iterations of $f$.
  But we have a better algorithm in this case:
  since at least one of the $x_k$ is zero by \refeq{logder},
  then $f^n(x_k = 0) = x_{n+k} = 0$, which provides
  the desired equation of $R$ \cite{strogatz}.
\end{remark}

@@

The algorithm was coded into a Mathematica program,
which was used to compute the polynomials for $n$ up to 13.
The polynomials for a general $\lambda$
and those at $\lambda = \pm1$ (onset and bifurcation points) are listed
in \reftab{Anlog} and \reftab{Pnlog}, respectively, for some small $n$.
%
For complex $R$, $\lambda$, and $\vx$,
the method can also compute the region of stability for $R$
  (i.e., the inverted Mandelbrot set),
with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
  instead of $\pm1$.
%the results are shown in \reffig{logbulb}
%for $n$ up to $8$.
%
For polynomials of larger $n$, see the website in \refsec{end}.
The representative $r$ values are listed in \reftab{rval}.

@@

\begin{remark}
The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
%
On the complex domain, however, we can have a $c$-fold branching with $c>2$,
  which corresponds to a contact points between ``bulbs''
  in the inverted Mandelbrot set, see \reffig{logbulb}.
\end{remark}
